### 2020-05-22 writeup/setup.tex
edits

\paragraph{Hypothesis on Heterogeneous Task Data}

Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}. %\todo{Add some references to add spice on these takes.}
We consider two natural questions within each category.
\begin{itemize}
	\item \textbf{Model shift.}
	In general the single-task models can also be different across different tasks.
We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.

	Under model shift, when do we get positive vs. negative transfer?
	How does the type of transfer depend on the number of data points, the distance of the task models etc?
	\item \textbf{Covariate shift.}
	The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
This is also known as covariate shift in the literature.
	How does covariate shift affect the rate of information transfer?
	For example, is it better to have the same covariance matrix or not?
\end{itemize}

>>>>

%\paragraph{Hypothesis on Heterogeneous Task Data}

%Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}. %\todo{Add some references to add spice on these takes.}
%We consider two natural questions within each category.
%\begin{itemize}
%	\item \textbf{Model shift.}
%	In general the single-task models can also be different across different tasks.
%We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.

%	Under model shift, when do we get positive vs. negative transfer?
%	How does the type of transfer depend on the number of data points, the distance of the task models etc?
%	\item \textbf{Covariate shift.}
%	The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
%This is also known as covariate shift in the literature.
%	How does covariate shift affect the rate of information transfer?
%	For example, is it better to have the same covariance matrix or not?
%\end{itemize}
